ICT and Future Productivity \\ Evidence and Theory of a GPT

### 2018-11-14 Latex/Conference_Zurich_Dec2018/Slides_Dec2018.tex
edited one bit of presentation for december

	\item ICT and productivity 
		\begin{itemize}
		\item Jorgenson \& Stiroh (1999), Oliner \& Stichel (2000),  Brynjolffson \& Lorin (2000), Stiroh (2002) %Brynjolffson \& Yang (1999) %use stock market valuations of firms to identify the value of IT assets
		\end{itemize}

@@

	\begin{itemize}
	\item ICT value added is less than 5\% of GDP (BEA, April 2018).

>>>>

	\item ICT and productivity 
		\begin{itemize}
		\item Jorgenson \& Stiroh (1999), Oliner \& Sichel (2000),  Brynjolffson \& Lorin (2000), Stiroh (2002) %Brynjolffson \& Yang (1999) %use stock market valuations of firms to identify the value of IT assets
		\end{itemize}

@@

	\item ICT shocks fluctuations are small (recovered shocks in VAR and model are small)

	\item ICT value added is less than 5\% of GDP (BEA, April 2018).
